A tool set for random number generation on GPUs in R

### 2022-01-02 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
p1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3081 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

There are a few important notes on the usage of these functions. (1), Users should run the function \fct{setBaseCreator} once at the very beginning of a \proglang{R} session if they would like to choose their own initial seeds. If \fct{setBaseCreator} is not called before \fct{createStreamsCpu} or \fct{createStreamsGpu}, then streams are created using the package's default initial seed. (2), Users may choose either \fct{createStreamsCpu} or \fct{createStreamsGpu} to run and must stick with that choice for their entire program, switching between \fct{createStreamsCpu} and \fct{createStreamsGpu} in the same program will create some of the streams twice.  When you create a new stream, it should not have the same seed as another existing stream, just like when you create a new car, it must have a distinct serial number. Streams should be created only once, and moved or copied if needed.

>>>>

There are a few important notes on the usage of these functions. (1), Users should run the function \fct{setBaseCreator} once at the very beginning of a \proglang{R} session if they would like to choose their own initial seeds. If \fct{setBaseCreator} is not called before \fct{createStreamsCpu} or \fct{createStreamsGpu}, then streams take the package's default initial seed. (2), Users may choose either \fct{createStreamsCpu} or \fct{createStreamsGpu} to run and must stick with that choice for their entire program, switching between \fct{createStreamsCpu} and \fct{createStreamsGpu} in the same program results in creating some of the streams twice.  A newly created stream should not have the same seed as another existing stream, just like when you create a new car, it must have a distinct serial number. Streams should be created only once, and moved or copied if needed.
